---
title: "Johnathan Jia's resume"
author: Johnathan Jia
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: false
    css:
      - css/custom_resume.css #custom resume functions
      - css/styles.css #override styles
      - resume #default file
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)

# ======================================================================
# These variables determine how the the data is loaded and how the exports are
# done.

# Is data stored in google sheets? If no data will be gather from the csv/
# folder in project
using_googlesheets <- TRUE

# Just the copied URL from the sheet
positions_sheet_loc <- "https://docs.google.com/spreadsheets/d/1Dw4SfMmSLxjvs8-slv77KVzospBS7cglQBV2NAXlAGY/"

# Is this sheet available for anyone to read? If you're using a private sheet
# set this to false and go to gather_data.R and run the data loading manually
# once to cache authentication
sheet_is_publicly_readable <- FALSE

# Is the goal of this knit to build a document that is exported to PDF? If so
# set this to true to have links turned into footnotes at the end of the
# document
PDF_EXPORT <- FALSE

# A global (gasp) variable that holds all the links that were inserted for
# placement at the end
links <- c()

# ======================================================================
# Now we source two external scripts. One contains functions for building the
# text output and the other loads up our data from either googlesheets or csvs

# Functions for building sections from CSV data
source('parsing_functions.R') 

# Load data for CV/Resume
source('gather_data.R')

# Now we just need to filter down the position data to include less verbose
# categories and only the entries we have designated for the resume
position_data <- position_data %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research', 'industry') ~ 'positions', 
      section %in% c('data_science_writings', 'by_me_press') ~ 'writings',
      TRUE ~ section
    )
  )

  # also filter the skills categories
skills <- skills %>% filter(in_resume) 
```

Aside
================================================================================

Contact Info {#contact}
--------------------------------------------------------------------------------
```{r}
contact_info %>% glue_data("- <i class='fa fa-{icon}'></i> <a href='{contact}'>{text}</a>")
```

Languages {#langs}
--------------------------------------------------------------------------------
```{r}
build_skill_bars(skills, "language")
```

Packages {#pkgs}
--------------------------------------------------------------------------------
```{r}
build_skill_bars(skills, "package")
```

Publications {#publications}
--------------------------------------------------------------------------------

#### Deep learning for detecting and elucidating human T-cell leukemia virus type 1 integration sites (Cell Patterns 2023)
##### H.Xu and **J.Jia**, H.Jeong,Z.Z

#### Delineating COVID-19 immunological features using single-cell RNA sequencing (The Innovation 2022)
##### W.Liu, **J.Jia**, Y.Dai, W.Chen, G.Pei,Q.Yan, Z.Zhao

#### Investigating Cellular Trajectories in the Severity of COVID-19 and Their Transcriptional Programs Using Machine Learning Approaches (Genes 2021)
##### H.Jeong and **J.Jia**, Y.Dai, L.Simon, Z.Zhao

#### What Controls the Acute Viral Infection Following Yellow Fever Vaccination? (Bulletin of Mathematical Biology 2016)
##### J.Moore, H.Ahmed, **J.Jia**, R.Akondy, R.Ahmed, R.Antia


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.

Main
================================================================================

Johnathan Jia {#title}
--------------------------------------------------------------------------------
### Data scientist interested in development and implementation of new deep learning algorithms
```{r}
#print_text_block(text_blocks, 'intro')
```

Professional Experience {data-icon=none}
--------------------------------------------------------------------------------
```{r}
position_data %>% print_section('positions')
```

Education {data-icon=none data-concise=true}
--------------------------------------------------------------------------------
```{r}
position_data %>% print_section('education')
```

Awards {data-icon=none}
--------------------------------------------------------------------------------
```{r}
print_awards(honors_awards)
```