---
title: "Johnathan Jia's resume"
author: Johnathan Jia
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: false
    css:
      - css/custom_resume.css #custom resume functions
      - css/styles.css #override styles
      - resume #default file
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)

# ======================================================================
# These variables determine how the the data is loaded and how the exports are
# done.

# Is data stored in google sheets? If no data will be gather from the csv/
# folder in project
using_googlesheets <- FALSE

# Just the copied URL from the sheet
positions_sheet_loc <- "https://docs.google.com/spreadsheets/d/14MQICF2F8-vf8CKPF1m4lyGKO6_thG-4aSwat1e2TWc"

# Is this sheet available for anyone to read? If you're using a private sheet
# set this to false and go to gather_data.R and run the data loading manually
# once to cache authentication
sheet_is_publicly_readable <- TRUE

# Is the goal of this knit to build a document that is exported to PDF? If so
# set this to true to have links turned into footnotes at the end of the
# document
PDF_EXPORT <- FALSE


# A global (gasp) variable that holds all the links that were inserted for
# placement at the end
links <- c()

# ======================================================================
# Now we source two external scripts. One contains functions for building the
# text output and the other loads up our data from either googlesheets or csvs

# Functions for building sections from CSV data
source('parsing_functions.R') 

# Load data for CV/Resume
source('gather_data.R')

# Now we just need to filter down the position data to include less verbose
# categories and only the entries we have designated for the resume
position_data <- position_data %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions', 
      section %in% c('data_science_writings', 'by_me_press') ~ 'writings',
      TRUE ~ section
    )
  ) 
```


Aside
================================================================================


![Johnathan Jia](https://avatars.githubusercontent.com/u/83188410?v=4){width=80%}


Contact Info {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> jdjia93@gmail.com  
- <i class="fa fa-github"></i> [github.com/jjia1](https://github.com/jjia1)
- <i class="fa fa-phone"></i> 832-361-0388

Skills {#skills}
--------------------------------------------------------------------------------
```{r}
build_skill_bars(skills)
```

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.


Main
================================================================================

Johnathan Jia {#title}
--------------------------------------------------------------------------------
### Currently searching for fulltime position

I am currently working fulltime as a data analyst in the Liu lab at Baylor College
of Medicine. My current projects include QC and analysis of brain organoid scRNA-seq
data. I am also currently involved in an IMC project, working to enhance cancer signals
using pipelines in Python. I am interested in a fulltime position as a data scientist 
with broad interests including machine/deep learning, big data analysis, and LLMs.

Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Data Analyst Associate

Baylor College of Medicine
Liu Lab

Houston, TX

Jan 2023 - Current

::: concise
- QC and analyzed scRNA-seq data from brain organoid tissues
- Developed pipelines in Python and R for use
- Pipeline for IMC Data Analysis 
:::

### Research Assistant I

MD Anderson Cancer Center
Immunotherapy Platform

Houston, TX

April 2019 - August 2020

- Collected and prepared samples of blood, bone marrow, and tumor for storage and analysis

Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

### Graduate Research Assistant

UT Health Science Center at Houston Graduate School of Biomedical Sciences
Zhao Lab

Houston, TX

January 2020 - December 2022

::: concise
- Developed DeepHTLV
- Analyzed COVID-19 scRNA-seq data transcriptional programs using DrivAER
- Wrote review of current COVID-19 scRNA-seq research
:::

### Undergraduate Research Assistant 

Emory University
Antia Lab

Emory University 

January 2012 - May 2015

- Used deterministic and stochastic predator-prey equations to model viral infection dynamics

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### University of Texas Health Science Center at Houston Graduate School of Biomedical Sciences

M.S. in Quantitative Sciences

Houston, TX

August 2020 - December 2022

Thesis: DeepHTLV: a deep learning model for detecting and elucidatinghuman T-cell
leukemia virus type 1 integration sites

### University of Texas Health Science Center McGovern School of Medicine

Houston, TX

August 2015 - May 2018

### Emory University

B.S. in Biology with High Honors, B.A. in Chemistry

Houston, TX

August 2011 - May 2015

Thesis: Investigating heterogeneity in the dynamics of virus and immune response
following a yellow fever vaccination


Publications {data-icon=file}
--------------------------------------------------------------------------------

### Deep learning for detecting and elucidating human T-cell leukemia virus type 1 integration sites 

Cell Patterns

Houston, TX

2023

Haodong Xu and **Johnathan Jia**, Hyun-Hwan Jeong,Zhongming Zhao

### Review of COVID-19 scRNA-seq technologies

The Innovation

Houston, TX

2022 

Wendao Liu, **Johnathan Jia**, Yulin Dai, Wenhao Chen, Guangsheng Pei,Qiheng Yan, Zhongming Zhao

### Investigating Cellular Trajectories in the Severity of COVID-19 and Their Transcriptional Programs Using MachineLearning Approaches

Genes

Houston, TX

2021

Hyun-Hwan Jeong and **Johnathan Jia**, Yulin Dai, LukasSimon, Zhongming Zhao

### What Controls the Acute Viral Infection Following Yellow Fever Vaccination?

Bulletin of mathematical biology

James Moore, Hasan Ahmed, **Johnathan Jia**, Rama Akondy, RafiAhmed, Rustom Antia

Honors and Awards {data-icon=certificate}
--------------------------------------------------------------------------------

### Best presentation at QS Seminar 

2022

Best QS seminar presentation 


### First prize at UTH GSBS Quantitative Sciences Retreat Poster Presentation

2022

First prize for pre-candidacy students

### Rheumatology Research Foundation Research Award

2026

Awarded for Shenzhen AS cohort research
